---
title: "Homework 5 - Zeynep Senveli"
author: "Zeynep Senveli"
date: "11/19/2017"
output: html_document
---

## Question 1
##### Reading in the Kamilar and Cooper dataset:
```{r}
library(curl)
require(car) 
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)  
```

##### Running a linear regression looking at the relationship between home range ($km^{2}$) and mean female body mass: 
```{r}
x <- log(d$Body_mass_female_mean)
y <- log(d$HomeRange_km2)
r <- lm(data = d, y ~ x)
confint(r)
cov2cor(vcov(r))
summary(r)
```
##### According to the results of the linear regression, my intercept is -9.44 and my slope is 0.67. The intercept is theoretically meaningless because it is negative when female body mass mean is zero... However, the slope means that with every unit change in mean female body mass, there's a 0.67 change in the home range.


## Question 2

#### Bootstrapping for linear regression using samples with replacement:
```{r}
bootstrap <- function(dat = d, mod.formula = formula(y ~ x)){
  dat.boot <- dat[sample(x = nrow(dat), size = nrow(dat), replace = TRUE),]
  boot.lm <- lm(mod.formula, data = dat.boot)
  coef(boot.lm)}
```

#### Performing 1000 iterations:
```{r}
s <- 1000 
vector.boot <- t(replicate(s, bootstrap()))
head(vector.boot)
```

#### Standard error of the estimates:
```{r}
apply(vector.boot, MARGIN = 2, sd)
```
##### For some reason, the sampling isn't working for me. I have used the code from a youtube tutorial on bootstrapping linear regression (with repeat), and here is the link to it just in case: https://www.youtube.com/watch?v=ydtOTctg5So. However, even though I have spent quite a bit of time troubleshooting, I can't seem to understand what the error is. But for what it's worth, I would expect my errors to go down because I'm using a reasonably big number of observations for the analysis. Technically, it should work fine but it's spitting out the same coefficients 1000 times instead of sampling new ones and I don't understand.

#### Percentile CIs 
```{r}
t(apply(vector.boot, MARGIN = 2, quantile, probs = c(0.025, 0.975)))
confint(r)
```
